% Acknowledgements
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\vspace{0.5cm}

First and foremost, I would like to express my deepest gratitude to my project supervisor, \textbf{[Supervisor Name]}, for their invaluable guidance, constant encouragement, and insightful feedback throughout this project. Their expertise in digital humanities and cultural preservation has been instrumental in shaping this work.

I am profoundly grateful to the \textbf{International Institute of Information Technology, Hyderabad}, particularly the Department of Computer Science and Engineering, for providing the academic environment and resources necessary to undertake this ambitious project.

My heartfelt thanks go to the countless musicians, ethnomusicologists, and cultural preservation organizations whose work has made this project possible. Special acknowledgment goes to the archives at \textbf{Sangeet Natak Akademi}, \textbf{Archives and Research Centre for Ethnomusicology (ARCE)}, and various state cultural departments for their invaluable documentation of India's musical heritage.

I extend my appreciation to the various online repositories, YouTube channels, and audio platforms that preserve traditional Indian music, making it accessible for educational and research purposes. The work of traditional musicians who continue to practice and teach these art forms despite modern challenges deserves particular recognition.

I am thankful to my family for their unwavering support and patience during the intensive research and development phases of this project. Their encouragement has been a constant source of motivation.

Finally, I acknowledge the rich musical traditions of India itself—the hereditary musicians, the \textit{guru-shishya parampara} (teacher-disciple tradition), the temple musicians, the folk artists, and the countless unnamed individuals who have preserved and passed down this invaluable cultural heritage through generations. This project is a humble attempt to document and honor their legacy in the digital age.

\vspace{1cm}

\begin{flushright}
\textbf{Priet Ukani}\\
[Your Roll Number]
\end{flushright}

\clearpage
